---
title: "Survey Work In Progress"
author: "Laurel Wee"
date: "2/1/2022"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(data.table)  # advanced pivot_table tools
library(naniar)      # replace NA tools
#library(sf)          # read in shapefiles
#library(tmap)        # interactive maps
#library(zipcodeR)    # for zipcode assignment by county
#library(raster)      # for mapping raster layers
#library(dplyr)       # needed ONLY if working on a windows computer
#library(ggwordcloud) # create wordcloud plots
library(patchwork)   # for stacking plots
library(kableExtra)  # for making tables
library(broom)
library(MASS)         #for ordered logist or probit regression
library(conflicted)  # allows for choosing preference over conflicting functions from different packages
library(RColorBrewer)
library(reshape)
library(lattice)
conflict_prefer("select", "dplyr")# use select function from tidyverse/dplyr package > from raster package
conflict_prefer("filter", "dplyr")
conflict_prefer("chisq.test", "janitor")
conflict_prefer("fisher.test", "janitor")
conflict_prefer("melt", "reshape")
```

```{r}
#load in compiled data files 

survey_data_tidy_sbv_filtered <- read.csv(here("data", "survey_data_tidy_sbv_filtered.csv"))

survey_data_tidy_sbv_long_filtered <- read.csv(here("data", "survey_data_tidy_sbv_long_filtered.csv"))
```
## demographic 

### Demographics 

Comparison of our survey demographics with demographics from Santa Barbara and Ventura Counties. 

##### Age


```{r load and prep sample demographics}

sample_margin <- survey_data_tidy_sbv_filtered
#Create sample margins
sample_margin$q31 <- as.integer(sample_margin$q31)

#create bins for age
labs <- c(paste(seq(0, 95, by = 5), seq(0 + 5 - 1, 100 - 1, by = 5),
                sep = "-"), paste(100, "+", sep = ""))

sample_margin<- sample_margin%>% 
  mutate(age= 2022- q31) 

#sample_margin$age_group <- cut(age$age, breaks = c(seq(0, 100, by = 5), Inf), labels = labs, right = FALSE)

```

```{r womens age demographics}
#sample data: Women
female <- sample_margin%>% 
  filter(q32 == "Woman") %>% 
  group_by(age_group) %>% 
  summarize(count = round(sum(weight)))  

#female_noround <- sample_margin%>% 
  #filter(q32 == "Woman") %>% 
  #group_by(age_group) %>% 
 #summarize(count = sum(weight))

total_female_sample <-sum(female$count)
#sum(female_noround$count)
#noround is to check rounding

female_sample <-female %>% 
  mutate(proportion = count/total_female_sample)
```


```{r men age demographics}
#sample data: male age
male <- sample_margin %>% 
  filter(q32 == "Man") %>% 
  group_by(age_group) %>% 
  summarize(count = round(sum(weight)))
  

total_male_sample <-sum(male$count)

male_sample <-male %>% 
  mutate(proportion = count/total_male_sample)

```
```{r}
ggplot
```

```{r population demographics}
#values from ACS 2019 combined for SB and V counties
sex_ratio_female_to_male <- 1.01
total_pop <- 1292505 #total population of Ventura and Santa Barbara Counties
total_female <- 650714 #total female population of the two counties
total_male <- 641791  #total male population of the two counties

#load American Community Survey 2019 Data 
ACS_age <- read.csv(here("data", "census", "age_range.csv"))
ACS_sex <- read.csv(here("data", "census", "total_population.csv"))
ACS_age <- ACS_age %>% 
  mutate(proportion = Total/total_pop)

#Age distributions by sex for men
male_dist <- read.csv(here("data", "census", "male_age proportions.csv")) 

#rename colomns
colnames(male_dist) <- c("age_group", "Santa Barbara", "Ventura", "Total")

#add a proprotion column
male_dist <- male_dist%>% 
  select("age_group", "Total") %>% 
  mutate(proprotion = Total/total_male) %>% #find proportion 
  #change column names to match grouping
      mutate(age_group = case_when(age_group == "Under 5 years" ~"0-5", 
                           age_group == "5 to 9 years" ~ "5-9",
                           age_group == "10 to 14 years" ~ "10-14",
                           age_group == "15 to 19 years" ~ "15-19",
                           age_group == "20 to 24 years" ~ "20-24",
                           age_group == "25 to 29 years" ~ "25-29",
                           age_group == "30 to 34 years" ~ "30-34",
                           age_group == "35 to 39 years" ~ "34-39",
                           age_group == "40 to 44 years" ~ "40-44",
                           age_group == "45 to 49 years" ~ "45-49",
                           age_group == "50 to 54 years" ~ "50-54",
                           age_group == "55 to 59 years" ~ "55-59",
                           age_group == "60 to 64 years" ~ "60-64",
                           age_group == "65 to 69 years" ~ "65-69",
                           age_group == "70 to 74 years" ~ "70-74",
                           age_group == "75 to 79 years" ~ "75-79",
                           age_group == "80 to 84 years" ~ "80-84",
                           age_group == "85 and over " ~ "85-100"))%>% 
  #filter out people under 18
  filter(!(age_group %in% c("0-5","5-9","10-14")))

#Age distribution for womn
female_dist <- read.csv(here("data", "census", "female_age_total.csv")) 
colnames(female_dist) <- c("age_group", "Santa Barbara", "Ventura", "Total")
  
female_dist <-female_dist %>% 
   select("age_group", "Total") %>% 
    mutate(proprotion = Total/total_female) %>% 
    mutate(age_group = case_when(age_group == "Under 5 years" ~"0-5",
                           age_group == "5 to 9 years" ~ "5-9",
                           age_group == "10 to 14 years" ~"10-14",
                           age_group == "15 to 19 years" ~"15-19",
                           age_group == "20 to 24 years" ~"20-24",
                           age_group == "25 to 29 years" ~"25-29",
                           age_group == "30 to 34 years" ~"30-34",
                           age_group == "35 to 39 years" ~"34-39",
                           age_group == "40 to 44 years" ~"40-44",
                           age_group == "45 to 49 years" ~"45-49",
                           age_group == "50 to 54 years" ~ "50-54",
                           age_group == "55 to 59 years" ~ "55-59",
                           age_group == "60 to 64 years" ~ "60-64",
                           age_group == "65 to 69 years" ~ "65-69",
                           age_group == "70 to 74 years" ~ "70-74",
                           age_group == "75 to 79 years" ~ "75-79",
                           age_group == "80 to 84 years" ~ "80-84",
                           age_group == "85 and over " ~ "85-100")) %>% 
  filter(!(age_group %in% c("0-5","5-9","10-14")))

```

```{r}
ggplot(mapping = aes(x=age_group))+
  geom_bar(data=female_dist,fill="red",width=0.1,position = position_nudge(0.22))+
  geom_bar(data=female_sample,fill="blue",width=0.1,position = position_nudge(-0.22))
```

## Statistical tests


# 3. Perception: 

*Question:* Does perception of aquaculture change when specifying seaweed aquaculture? 

*Hypothesis:* Yes, perception of seaweed aquaculture will be more positive than aquaculture more broadly. 

*Statistical Test:* Chi-square test of Q12 vs. Q13

```{r}
# Pull Q 12 and Q13 on perception of aquaculture and seaweed aquaculture, assign numerical value to categorical response
perception_counts <- survey_data_tidy_sbv_filtered %>% 
  select(question, answer) %>% 
  filter(question == "q12" | 
         question == "q13") %>% 
  mutate(number = case_when( 
    answer == "Very Negative" ~ 1,
    answer == "Negative" ~ 2,
    answer == "Neutral" ~ 3,
    answer == "Positive" ~ 4,
    answer == "Very Positive" ~ 5,
    answer == "Unsure/Not familiar" ~ 6)) %>%
  mutate_all(na_if,"")
# get means
perception_q12<- perception_counts %>% 
  filter(question == "q12") %>% 
  pull(number)
perception_q13 <- perception_counts %>% 
  filter(question == "q13") %>% 
  pull(number)

# Create a table with counts
perception_counts_table <- perception_counts %>% 
  tabyl(question, answer) %>% 
  filter(question == "q12" | 
         question == "q13") %>% 
  select(-NA_)
perception_counts_table
# atleast 80% of cells <=5 is satisfied
```

## Environmental Impacts

```{r}
# Environmental Impacts Questions

# Q23_1 - Q23_7
# To what extent do you agree with each of the following statements?

environ_impacts <- survey_data_tidy_sbv_long_filtered %>% 
  select(question, answer) %>% 
  filter(question == "q23_1" | 
           question == "q23_2" |
           question == "q23_3" |
           question == "q23_4" |
           question == "q23_5" |
           question == "q23_6" |
           question == "q23_7") %>% 
  mutate(question = case_when( 
    question == "q23_1" ~ "...has negative impacts on marine ecosystems.", #risk
    question == "q23_2" ~ "...improves water quality nearby.", #benefit
    question == "q23_3" ~ "...infrastructure poses a risk to marine life.", #risk
    question == "q23_4" ~ "...infrastructure has positive impacts on marine ecosystems.", #benefit
    question == "q23_5" ~ "...has positive impacts on marine ecosystems.", #take out because only qualtrics was asked
    question == "q23_6" ~ "...causes bad smells nearby.", #risk
    question == "q23_7" ~ "...is visually appealing.")) %>% #benefit
  mutate(number = case_when( 
    answer == "Strongly Disagree" ~ 1,
    answer == "Disagree" ~ 2,
    answer == "Neutral" ~ 3,
    answer == "Agree" ~ 4,
    answer == "Strongly Agree" ~ 5,
    answer == "Don't know" ~ 6)) %>%
  #replace_with_na(replace = list(number = -999)) %>% 
  drop_na() %>%                                            # drop NAs (counts of those who skipped question)
  #mutate_all(na_if, "") %>% 
  group_by(question, answer, number) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  group_by(question) %>% 
  mutate(proportion = (count / sum(count))*100) %>% 
  ungroup() 

# Specify categorical order of answers
environ_impacts$answer <- factor(environ_impacts$answer, levels = c("Don't know",
                                                                    "Strongly Disagree", 
                                                                    "Disagree", 
                                                                    "Neutral",
                                                                    "Agree",
                                                                    "Strongly Agree"
                                                                    ))

environ_impacts_risk <- environ_impacts %>% 
  filter(question == "...has negative impacts on marine ecosystems." |
           question == "...infrastructure poses a risk to marine life." |
           question == "...causes bad smells nearby.")

environ_impacts_benefit <- environ_impacts %>% 
  filter(question == "...improves water quality nearby."|
           question == "...infrastructure has positive impacts on marine ecosystems."|
           question == "...is visually appealing.")
```


```{r}
# percent stacked barchart
ggplot(data = environ_impacts_benefit, 
       aes(fill = forcats::fct_rev(answer), 
           y = proportion,
           x = question)) +
  geom_bar(position = "fill",
           stat = "identity", 
           width = .8) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(position = "top") +
  scale_fill_manual(values =c("#2C7BB6","#ABD9E9","#FFFFBF","#FDAE61","#D7191C","#C0C0C0"))+
  labs(x = "",
       y = "",
       title = "Seaweed Aquaculture...") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        #axis.text.x=element_blank()# if you want to remove the bar labels
        )+
  guides(fill=guide_legend(nrow=1,byrow=TRUE))


ggplot(data = environ_impacts_risk, 
       aes(fill = forcats::fct_rev(answer), 
           y = proportion,
           x = question)) +
  geom_bar(position = "fill",
           stat = "identity",
           width = .8) +
  scale_y_continuous(labels = scales::percent) +
  #scale_x_discrete(position = "right") +
  scale_fill_manual(values =c("#2C7BB6","#ABD9E9","#FFFFBF","#FDAE61","#D7191C","#C0C0C0"))+
  labs(x = "",
       y = "",
       title = "Seaweed Aquaculture...") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        #axis.text.x=element_blank() # if you want to remove the bar labels
        )+
  guides(color = guide_legend(reverse=TRUE),fill=guide_legend(nrow=1,byrow=TRUE))
```

```{r}
# demographic analysis for Qualtrics survey

# split up support/opposed responses by answer
sbv_residents_edu <- survey_data_tidy_sbv_long_filtered %>% 
  filter(response_type != 3) %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  group_by(q34, answer) %>% #select education level question
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))

# Specify categorical order of questions and answers
sbv_residents_edu$answer <- factor(sbv_residents_edu$answer, levels = c("Strongly opposed", 
                                                                                        "Somewhat opposed", 
                                                                                        "Neither opposed nor in support",
                                                                                        "Somewhat supportive",
                                                                                        "Strongly supportive"))

# percent stacked barchart
ggplot(data = sbv_residents_edu, 
       aes(fill = forcats::fct_rev(answer),
           y = proportion,
           x = q34)) +
  geom_bar(position = "stack",
           stat = "identity",
           width = 0.5) +
  scale_y_continuous(labels = scales::percent) +
  #scale_fill_brewer(type = "div",
                    #palette = "RdYlGn",
                    #direction = -1) +
  scale_fill_manual(values =c("#2C7BB6","#ABD9E9","#FFFFBF","#FDAE61","#D7191C")) +
  labs(x = "",
       y = "",
       title = "Are you supportive of or opposed to expanding \nseaweed aquaculture off the California coast?") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "right") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```
```{r}
# demographic analysis for Qualtrics survey

# split up support/opposed responses by answer
sbv_residents_income <- survey_data_tidy_sbv_long_filtered %>% 
  filter(response_type != 3) %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  group_by(q35, answer) %>% #select education level question
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))

# Specify categorical order of questions and answers
sbv_residents_income$answer <- factor(sbv_residents_income$answer, levels = c("Strongly opposed", 
                                                                                        "Somewhat opposed", 
                                                                                        "Neither opposed nor in support",
                                                                                        "Somewhat supportive",
                                                                                        "Strongly supportive"))

# percent stacked barchart
ggplot(data = sbv_residents_income, 
       aes(fill = forcats::fct_rev(answer),
           y = proportion,
           x = q35)) +
  geom_bar(position = "stack",
           stat = "identity",
           width = 0.5) +
  scale_y_continuous(labels = scales::percent) +
  #scale_fill_brewer(type = "div",
                    #palette = "RdYlGn",
                    #direction = -1) +
  scale_fill_manual(values =c("#2C7BB6","#ABD9E9","#FFFFBF","#FDAE61","#D7191C")) +
  labs(x = "",
       y = "",
       title = "Are you supportive of or opposed to expanding \nseaweed aquaculture off the California coast?") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "right") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```


```{r}
#q34
# opposed residents
opposed_residents_edu <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  filter(answer == "Strongly opposed" |
           answer == "Somewhat opposed") %>% 
  group_by(answer, q34) %>% 
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))

# supportive residents
supportive_residents_edu <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  filter(answer == "Strongly supporitve" |
           answer == "Somewhat supportive") %>% 
  group_by(answer, q34) %>% 
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))
  
# neutral residents
neutral_residents_edu <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  filter(answer == "Neither opposed nor in support") %>% 
  group_by(answer, q34) %>% 
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))
```

```{r}
#q35
# opposed residents
opposed_residents_income <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  filter(answer == "Strongly opposed" |
           answer == "Somewhat opposed") %>% 
  group_by(answer, q35) %>% 
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))

# supportive residents
supportive_residents_income <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  filter(answer == "Strongly supporitve" |
           answer == "Somewhat supportive") %>% 
  group_by(answer, q35) %>% 
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))
  
# neutral residents
neutral_residents_income <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2")) %>% 
  filter(answer != "") %>% 
  drop_na() %>% 
  filter(answer == "Neither opposed nor in support") %>% 
  group_by(answer, q35) %>% 
  summarize(count = n()) %>% 
  mutate(proportion = (count / sum(count)))
```