---
title: "Survey Data Exploration"
author: "Sydney Rilum"
date: "12/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load necessary packages
library(tidyverse)
library(here)
library(janitor)
library(data.table)  # advanced pivot_table tools
library(naniar)      # replace NA tools
library(sf)          # read in shapefiles
#library(tmap)        # interactive maps
library(zipcodeR)    # for zipcode assignment by county
#library(raster)      # for mapping raster layers
#library(dplyr)       # needed ONLY if working on a windows computer
library(ggwordcloud) # create wordcloud plots
library(wordcloud)
library(patchwork)   # for stacking plots
library(kableExtra)  # for making tables

#library(conflicted)  # allows for choosing preference over conflicting functions from different packages
#conflict_prefer("select", "dplyr") # use select function from tidyverse/dplyr package > from raster package
#conflict_prefer("filter", "dplyr")
```

# Data Set-up & Cleaning 

```{r}
# Read in combined survey data
survey_data <- read.csv(here("data","survey_data","combined_survey_responses.csv"))

survey_data_tidy <- survey_data %>%
  clean_names() %>% 
  slice(-1) # remove first row of df
```

```{r}
# Read in the Qualtrics Survey data
#survey_data_qualtrics <- read.csv(here("data","survey_data","qualtrics_survey_responses_final.csv"))

# Read in the QR code Survey data
#survey_data_qrcode <- read.csv(here("data","survey_data","QRcode_choice_text_January13,2022.csv"))

# Clean up dataframes
#survey_data_qualtrics_tidy <- survey_data_qualtrics %>%
#  clean_names() %>% 
#  slice(-1) # remove first row of df

#survey_data_qrcode_tidy <- survey_data_qrcode %>%
#  clean_names() %>% 
#  slice(-(1:2)) %>% # remove first 2 rows of df
#  select(-recipient_last_name, # remove empty/unnecessary columns
#         -recipient_first_name,
#         -recipient_email,
#         -external_reference,
#         -distribution_channel,
#         -user_language,
#         -status)
```

```{r}
# Convert dataframe to tidydata format (Reshaping the data)

# convert data frame into a data table
survey_data_tidy <- as.data.table(survey_data_tidy)

# use melt() from `datatable` package (advanced version of pivot_longer()) to reshape data from wide to long format
# unlike pivot_longer(), melt() allows for pivoting data tables with both numeric and character data!
survey_data_tidy_long <- survey_data_tidy %>% 
  melt(id.vars = c("response_id", "response_type", "finished"), 
       variable.name = "question", 
       value.name = "answer")
```

## Filter for Santa Barbara & Ventura County Zipcodes 

```{r}
# Q37 - Zipcode Data

# Create a dataframe containing only zipcodes from Ventura and Santa Barbara Counties

## Not run:
download_zip_data() # uses zipcodeR data 
## End(Not run)

ventura_co_zip_full <-
  search_county("ventura", "CA") 

ventura_zipcodes<- 
  ventura_co_zip_full[,c("zipcode", "county", "lat", "lng")]

sb_co_zip_full <- 
 search_county("Santa Barbara", "CA")

sb_zipcodes<- 
  sb_co_zip_full[,c("zipcode", "county", "lat", "lng")]

# combine SB & Ventura zipcode data frames
sb_ventura_co_zip <- 
  rbind(ventura_zipcodes, sb_zipcodes)
```

```{r}
# select survey responses from Ventura and Santa Barbara Counties ONLY
survey_data_tidy_sbv <- merge(survey_data_tidy, sb_ventura_co_zip, 
                              by.x = "q37", by.y = "zipcode")

### Convert dataframe to tidydata format (Reshaping the data)

# convert data frame into a data table
survey_data_tidy_sbv <- as.data.table(survey_data_tidy_sbv)

# use melt() from `datatable` package (advanced version of pivot_longer()) to reshape data from wide to long format
survey_data_tidy_sbv_long <- survey_data_tidy_sbv %>% 
  melt(id.vars = c("response_id", "response_type", "finished"), 
       variable.name = "question", 
       value.name = "answer")
```

## Filter Survey Response Type

Response Types Key:

0 = speeders (time removal)
1 = completes (approved by our team)
2 = removed by our team for replacement (flagged for not answering ranking questions, but otherwise fine)
3 = response collected via our own outreach (QRcode/email/social media)

(Note: Qualtrics Paid Responses = 0,1,2)

```{r}
# count number of:

# 0 (speeders)
response_0 <- survey_data_tidy %>% 
  filter(response_type == 0)         # 15 speeders
  
# 1 (completes)
response_1 <- survey_data_tidy %>% 
  filter(response_type == 1)         # 302 completes

# 2 (replaced)
response_2 <- survey_data_tidy %>% 
  filter(response_type == 2)         # 48 extra completes

# 3 (responses collected via email/social media)
response_3 <- survey_data_tidy %>% 
  filter(response_type == 3)         # 146 responses via self-distribution

# 3 completes (finished survey)
response_3_completes <- survey_data_tidy %>% 
  filter(response_type == 3) %>% 
  filter(finished == TRUE)           # 110 completes

# 3 incompletes (did not finish survey)  
response_3_incompletes <- survey_data_tidy %>% 
  filter(response_type == 3) %>% 
  filter(finished == FALSE)          # 36 incompletes

# Total number of responses = 511
# Total number of responses (-speeders) = 496
# Total number of responses (-speeders, -incompletes) = 460

# Total number of SB/Ventura County responses = 400 
# Total number of SBV responses (-speeders) = 389
response_sbv <- survey_data_tidy_sbv %>% 
  filter(response_type != 0) 

```

```{r}
# remove speeders responses (response type: 0) from survey dataframes
survey_data_tidy_filtered <- survey_data_tidy %>% 
  filter(response_type != 0)

survey_data_tidy_long_filtered <- survey_data_tidy_long %>% 
  filter(response_type != 0)

# remove speeders from SBV datasets
## THESE DATASETS SHOULD BE SAVED AS CSVs (see next code chunk)
survey_data_tidy_sbv_filtered <- survey_data_tidy_sbv %>% 
  filter(response_type != 0) 

survey_data_tidy_sbv_long_filtered <- survey_data_tidy_sbv_long %>% 
  filter(response_type != 0)
```

## Save Finalized Data Frames as csv 

```{r}
write.csv(survey_data_tidy_sbv_filtered,
          file = here("data", "survey_data_tidy_sbv_filtered.csv"))

write.csv(survey_data_tidy_sbv_long_filtered,
          file = here("data", "survey_data_tidy_sbv_long_filtered.csv"))
```


## Map Survey Response Location by zipcode/county 

```{r}
# Read in California counties outline
#ca_counties <- read_sf(here("data", "ca_counties", "CA_Counties_TIGER2016.shp")) %>% 
#  clean_names()

# Read in US zipcodes tabulation areas
#us_zipcodes <- read_sf(here("data", "zipcode_tabulation_areas_2020", "tl_2021_us_zcta520.shp")) %>% 
#  clean_names()

```

```{r}
#us_zipcodes <- drop_na(us_zipcodes)

# Check class
#class(us_zipcodes$ztca5ce20) # character

# Crop US zipcodes data frame to include only CA zipcodes
#ca_zipcodes <- us_zipcodes %>% 
#  filter(ztca5ce20 > 90000,
#         ztca5ce20 < 95000)

# Check CRS (Coordinate Reference System)
#st_crs(ca_counties) # WGS 84
#st_crs(us_zipcodes) # NA
```

# Data Analysis

## Average time to take survey 

```{r}
# Check class
class(survey_data_tidy$duration_in_seconds) # character

# Convert class from character to numeric
survey_data_tidy$duration_in_seconds = as.numeric(survey_data_tidy$duration_in_seconds)

# Calculate time (in minutes) spent taking survey
mean((survey_data_tidy$duration_in_seconds)/60)  # check for outliers
median((survey_data_tidy$duration_in_seconds)/60) # positively skewed
min((survey_data_tidy$duration_in_seconds)/60) # potential outlier
max((survey_data_tidy$duration_in_seconds)/60) # potential outlier
```


## Wording Experiment - Does word choice influence residents' support for kelp aquaculture? 

```{r}
# Are you supportive of or opposed to expanding ______ off the California coast?
# q2 - seaweed farming
# q4 - kelp farming
# q6 - seaweed aquaculture
# q8 - kelp aquaculture

wording_exp <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8") %>% 
  mutate(answer = case_when( 
    answer == "Strongly opposed" ~ 1,
    answer == "Somewhat opposed" ~ 2,
    answer == "Neither opposed nor in support" ~ 3,
    answer == "Somewhat supportive" ~ 4,
    answer == "Strongly supportive" ~ 5)) %>% 
  filter(answer != "NA") 

# boxplot of wording experiment answers
ggplot(data = wording_exp, 
       aes(x = question,
           y = answer)) +
  coord_flip() +
  geom_boxplot() +
  stat_summary(fun = mean, 
               geom = "point", 
               shape = 20, 
               size = 3, 
               color = "black", 
               fill = "black") +
  labs(x = "Term",
       y = "Strongly Opposed to Strongly Supportive",
       title = "Are you supportive of or opposed to expanding ______ off the California coast?") +
  theme_light() +
  theme(legend.position = "none")

```

```{r}
# Descriptive statistics subset - wording experiment answer counts
wording_exp_counts <- wording_exp %>% 
  group_by(question) %>% 
  summarize(count1 = sum(answer == 1),
            count2 = sum(answer == 2),
            count3 = sum(answer == 3),
            count4 = sum(answer == 4),
            count5 = sum(answer == 5),
            sample_size = n())

# Are you supportive of or opposed to expanding ______ off the California coast?
# q2 - seaweed farming
# q4 - kelp farming
# q6 - seaweed aquaculture
# q8 - kelp aquaculture

# summary table
wording_exp_counts %>% 
  kable(col.names = c("Question", 
                      "Strongly opposed", 
                      "Somewhat opposed", 
                      "Neither opposed nor in support",
                      "Somewhat supportive",
                      "Strongly supportive",
                      "Sample Size")) %>% 
  kable_styling()



##### NOT RIGHT ??
## How do I get means..... for each question
wording_exp_stats <- wording_exp %>% 
  group_by(question) %>% 
  summarize(mean1 = round(mean(answer == 1),3),
            mean2 = round(mean(answer == 2),3),
            mean3 = round(mean(answer == 3),3),
            mean4 = round(mean(answer == 4),3),
            mean5 = round(mean(answer == 5),3))

```


### Word Clouds 

```{r}
# Word Cloud data cleaning

# convert each string of words to lowercase
survey_data_tidy$q3 <- tolower(survey_data_tidy$q3)  # seaweed farming
survey_data_tidy$q5 <- tolower(survey_data_tidy$q5)  # kelp farming
survey_data_tidy$q7 <- tolower(survey_data_tidy$q7)  # seaweed aquaculture
survey_data_tidy$q9 <- tolower(survey_data_tidy$q9)  # seaweed farming
```

```{r}
# q3 - seaweed farming
seaweed_farming <- survey_data_tidy %>% 
  select(q3) %>%
  mutate(q3 = str_trim(q3)) %>%  # remove excess whitespace before/after word
  mutate(q3 = str_replace(q3, pattern = "goodl", replacement = "good")) %>% 
  mutate(q3 = str_replace(q3, pattern = "auaculture", replacement = "auqaculture")) %>% 
  mutate(q3 = str_replace(q3, pattern = "sustainability", replacement = "sustainable")) %>% 
  filter(q3 != "idk") %>% 
  filter(q3 != "huh") %>% 
  filter(q3 != "none") %>% 
  filter(q3 != "nothing") %>% 
  count(q3) %>%                  # count repeating words
  arrange(-n)                    # arrange word counts from largest to smallest

wordcloud_seaweed_farming <- ggplot(data = seaweed_farming, 
                                    aes(label = q3)) +
  geom_text_wordcloud(aes(color = n, size = n), 
                      shape = "diamond") +
  scale_size_area(max_size = 25) +
  scale_color_gradientn(colors = c("burlywood4", "green")) +
  theme_minimal() +
  labs(title = "seaweed farming") 
  #theme(axis.line.y = element_line(color="black", size = 0.1))

# alternative word cloud
seaweed_farming_test <- seaweed_farming %>% 
  slice(-1) # remove first row of df

wordcloud_seaweed_farming_2 <- wordcloud(words = seaweed_farming_test$q3, 
                                         freq = seaweed_farming_test$n,
                                         min.freq = 1,
                                         random.order = FALSE,
                                         colors = brewer.pal(8, "Dark2")) 
```

```{r}
# q5 - kelp farming
kelp_farming <- survey_data_tidy %>% 
  select(q5) %>%
  mutate(q5 = str_trim(q5)) %>%  # remove excess whitespace before/after word
  mutate(q5 = str_replace(q5, pattern = "icean", replacement = "ocean")) %>% 
  filter(q5 != "i") %>% 
  filter(q5 != "idk") %>% 
  filter(q5 != "what") %>% 
  filter(q5 != "test") %>% 
  filter(q5 != "testpanel") %>%
  count(q5) %>%                  # count repeating words
  arrange(-n)                    # arrange word counts from largest to smallest


wordcloud_kelp_farming <- ggplot(data = kelp_farming, 
                                    aes(label = q5)) +
  geom_text_wordcloud(aes(color = n, size = n), 
                      shape = "diamond") +
  scale_size_area(max_size = 25) +
  scale_color_gradientn(colors = c("darkgreen", "green")) +
  theme_minimal() +
  labs(title = "kelp farming") +
  theme(plot.title.position = "panel")
  #theme(axis.line.x = element_line(color="black", size = 0.1),
        #axis.line.y = element_line(color="black", size = 0.1))

# alternative word cloud
kelp_farming_test <- kelp_farming %>% 
  slice(-1) # remove first row of df

wordcloud_kelp_farming_2 <- wordcloud(words = kelp_farming_test$q5, 
                                      freq = kelp_farming_test$n,
                                      min.freq = 1,
                                      random.order = FALSE,
                                      colors = brewer.pal(8, "Dark2"))
```

```{r}
# q7 - seaweed aquaculture
seaweed_aquaculture <- survey_data_tidy %>% 
  select(q7) %>%
  mutate(q7 = str_trim(q7)) %>%  # remove excess whitespace before/after word
  mutate(q7 = str_replace(q7, pattern = "enviironmental", replacement = "environment")) %>% 
  mutate(q7 = str_replace(q7, pattern = "enviroment", replacement = "environment")) %>% 
  mutate(q7 = str_replace(q7, pattern = "environments", replacement = "environment")) %>% 
  mutate(q7 = str_replace(q7, pattern = "harvesting", replacement = "harvest")) %>% 
  filter(q7 != "none") %>% 
  filter(q7 != "nothing") %>% 
  count(q7) %>%                  # count repeating words
  arrange(-n)                    # arrange word counts from largest to smallest


wordcloud_seaweed_aquaculture <- ggplot(data = seaweed_aquaculture, 
                                    aes(label = q7)) +
  geom_text_wordcloud(aes(color = n, size = n), 
                      shape = "diamond") +
  scale_size_area(max_size = 25) +
  scale_color_gradientn(colors = c("springgreen4", "green")) +
  theme_minimal() +
  labs(title = "seaweed aquaculture")

# alternative word cloud
seaweed_aquaculture_test <- seaweed_aquaculture %>% 
  slice(-1) # remove first row of df

wordcloud_seaweed_aquaculture_2 <- wordcloud(words = seaweed_aquaculture_test$q7, 
                                            freq = seaweed_aquaculture_test$n,
                                            min.freq = 1,
                                            random.order = FALSE,
                                            colors = brewer.pal(8, "Dark2"))
```

```{r}
# q9 - kelp aquaculture
kelp_aquaculture <- survey_data_tidy %>% 
  select(q9) %>%
  mutate(q9 = str_trim(q9)) %>%  # remove excess whitespace before/after word
  mutate(q9 = str_replace(q9, pattern = "aquaculter", replacement = "aquaculture")) %>% 
  mutate(q9 = str_replace(q9, pattern = "environment", replacement = "environmental")) %>% 
  mutate(q9 = str_replace(q9, pattern = "environmentalal", replacement = "environmental")) %>%   
  mutate(q9 = str_replace(q9, pattern = "sustainable", replacement = "sustainability")) %>%   
  filter(q9 != "huh") %>% 
  filter(q9 != "noidea") %>% 
  filter(q9 != "none") %>% 
  filter(q9 != "nope") %>% 
  filter(q9 != "unsure") %>% 
  count(q9) %>%                  # count repeating words
  arrange(-n)                    # arrange word counts from largest to smallest


wordcloud_kelp_aquaculture <- ggplot(data = kelp_aquaculture, 
                                    aes(label = q9)) +
  geom_text_wordcloud(aes(color = n, size = n), 
                      shape = "diamond") +
  scale_size_area(max_size = 25) +
  scale_color_gradientn(colors = c("yellow4", "green")) +
  theme_minimal() +
  labs(title = "kelp aquaculture") 
  #theme(axis.line.x = element_line(color="black", size = 0.1))

# alternative word cloud
kelp_aquaculture_test <- kelp_aquaculture %>% 
  slice(-1) # remove first row of df

wordcloud_kelp_aquaculture_2 <- wordcloud(words = kelp_aquaculture_test$q9, 
                                         freq = kelp_aquaculture_test$n,
                                         min.freq = 1,
                                         random.order = FALSE,
                                         colors = brewer.pal(8, "Dark2"))
```

```{r}
# stack word cloud plots using `patchwork` 
wordclouds <- ((wordcloud_seaweed_farming + wordcloud_seaweed_aquaculture) /
                 (wordcloud_kelp_farming + wordcloud_kelp_aquaculture))

wordclouds +
  plot_annotation(title = "When you think of _____  _____, what word comes to mind?") &
  theme(plot.title = element_text(size = 15)) 

```



### Ranking terms by positivity 

```{r}
# Q11_1 - Q11_8 (Aquaculture is referred to by many names. Please rank the following names based on which you view most positively, with 1 being most positive.)

# q11_1 - ocean farming
# q11_2 - seaweed farming
# q11_3 - kelp farming
# q11_4 - ocean aquaculture
# q11_5 - seaweed aquaculture
# q11_6 - kelp aquaculture
# q11_7 - regenerative aquaculture
# q11_8 - seaweed mariculture

# make new subset of data (WITH ALL SURVEY RESPONSES)
wording_exp_rank <- survey_data_tidy %>% 
  select(q11_1:q11_8) %>% 
  mutate_if(is.character,as.numeric) %>% 
  summarize_all(mean, na.rm = TRUE) # calculate mean rank score for each answer choice

# transpose dataframe
wording_exp_rank <- t(wording_exp_rank) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "term") %>% 
  mutate(term = case_when(
    term == "q11_1" ~ "ocean farming",
    term == "q11_2" ~ "seaweed farming",
    term == "q11_3" ~ "kelp farming",
    term == "q11_4" ~ "ocean aquaculture",
    term == "q11_5" ~ "seaweed aquaculture",
    term == "q11_6" ~ "kelp aquaculture",
    term == "q11_7" ~ "regenerative aquaculture",
    term == "q11_8" ~ "seaweed mariculture")) %>% 
  mutate(term = fct_reorder(term, V1, .desc = TRUE))  # order topics by count, smallest (most interested) to largest (least interested)

ggplot(data = wording_exp_rank, aes(x = term, y = V1)) +
  geom_col(fill = "skyblue2") +
  coord_flip() +
  theme_minimal() +
  labs(x = "",
       y = "Average Ranked Score (from 1 - 6, with 1 being most positive)",
       title = "Terminology Ranked by Most Positive Connotation")

```

```{r}
# Q11_1 - Q11_8 (Aquaculture is referred to by many names. Please rank the following names based on which you view most positively, with 1 being most positive.)

# q11_1 - ocean farming
# q11_2 - seaweed farming
# q11_3 - kelp farming
# q11_4 - ocean aquaculture
# q11_5 - seaweed aquaculture
# q11_6 - kelp aquaculture
# q11_7 - regenerative aquaculture
# q11_8 - seaweed mariculture


# make new subset of data USING SBV data ONLY
wording_exp_rank_2 <- survey_data_tidy_sbv_long_filtered %>% 
  select(question, answer) %>% 
  mutate_if(is.character,as.numeric) %>% 
  filter(question == "q11_1"|
           question == "q11_2"|
           question == "q11_3"|
           question == "q11_4"|
           question == "q11_5"|
           question == "q11_6"|
           question == "q11_7"|
           question == "q11_8") %>% 
  mutate(question = case_when(
    question == "q11_1" ~ "ocean farming",
    question == "q11_2" ~ "seaweed farming",
    question == "q11_3" ~ "kelp farming",
    question == "q11_4" ~ "ocean aquaculture",
    question == "q11_5" ~ "seaweed aquaculture",
    question == "q11_6" ~ "kelp aquaculture",
    question == "q11_7" ~ "regenerative aquaculture",
    question == "q11_8" ~ "seaweed mariculture")) %>% 
  drop_na() %>% 
  group_by(question) %>% 
  summarize(mean = round(mean(answer, na.rm = TRUE),2)) %>% # calculate mean rank score for each answer choice
  mutate(question = fct_reorder(question, mean, .desc = TRUE))  # order topics by count, smallest (most interested) to largest (least interested)


ggplot(data = wording_exp_rank_2, aes(x = mean, 
                                      y = question,
                                      fill = mean)) +
  geom_bar(stat = "identity",
           fill = "skyblue2") +
  geom_text(aes(label = mean),
            hjust = 1.5) +
  labs(y = "",
       x = "Average Ranked Score (from 1 - 6, with 1 being most positive)",
       title = "Terminology Ranked by Most Positive Connotation") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "none") 

#ggsave("rank_terms.png")
```


## Knowledge 

```{r fig.width = 5}
# (Q10) - How familiar are you with aquaculture?

familiarity <- survey_data_tidy_sbv_long_filtered %>% 
  select(question, answer) %>% 
  filter(question == "q10") %>% 
  group_by(answer) %>% 
  summarize(count = n())

# Specify categorical order of answers
familiarity$answer <- factor(familiarity$answer, levels = c("Never heard of it",
                                                            "Heard of it, but don't know details",
                                                            "Basic understanding",
                                                            "Very familiar"))

ggplot(data = familiarity, aes(x = count,
                               y = answer,
                               fill = answer)) +
  geom_bar(stat = "identity",
           fill = "lightsteelblue") + 
  geom_text(aes(label = count), hjust = 1.5) +
  labs(x = "count",
       y = "",
       title = "How familiar are you with aquaculture?") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "none") 
  
#ggsave("familiarity.png")
```



## Perception of Aquaculture vs. Seaweed Aquaculture 

```{r}
## Comparing perceptions

# (Q12) - In general, how positive or negative is your view of aquaculture?
# (Q13) - In general, how positive or negative is your view of seaweed aquaculture?

perception_aq_boxplot <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q12" | question == "q13") %>% 
  mutate(question = case_when( 
    question == "q12" ~ "aquaculture",
    question == "q13" ~ "seaweed aquaculture")) %>% 
  mutate(answer = case_when( 
    answer == "Very Negative" ~ -2,
    answer == "Negative" ~ -1,
    answer == "Neutral" ~ 0,
    answer == "Positive" ~ 1,
    answer == "Very Positive" ~ 2,
    answer == "Unsure/Not familiar" ~ -999)) %>%
  replace_with_na(replace = list(answer = -999))
  
# boxplot  
ggplot(data = perception_aq_boxplot, 
       aes(x = question,
           y = answer)) +
  coord_flip() +
  geom_boxplot(color = c("darkblue","springgreen4")) +
  stat_summary(fun = mean, 
               geom = "point", 
               shape = 20, 
               size = 3, 
               color = "black", 
               fill = "black") +
  labs(x = "",
       y = "Very Negative to Very Positive",
       title = "In general, how positive or negative is your view of ______ ?") +
  theme_light() +
  theme(legend.position = "none")

```

```{r}
# alternative data frame
perception_aq_stacked_bar <- survey_data_tidy_sbv_long_filtered %>% 
  select(question, answer) %>% 
  filter(question == "q12" | question == "q13") %>% 
  mutate(question = case_when( 
    question == "q12" ~ "aquaculture",
    question == "q13" ~ "seaweed aquaculture")) %>% 
  mutate(number = case_when( 
    answer == "Very Negative" ~ 1,
    answer == "Negative" ~ 2,
    answer == "Neutral" ~ 3,
    answer == "Positive" ~ 4,
    answer == "Very Positive" ~ 5,
    answer == "Unsure/Not familiar" ~ 6)) %>%
  drop_na() %>% 
  group_by(question, answer, number) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  group_by(question) %>% 
  mutate(proportion = (count / sum(count)))


# Specify categorical order of questions and answers
perception_aq_stacked_bar$answer <- factor(perception_aq_stacked_bar$answer, levels = c("Unsure/Not familiar", 
                                                                                        "Very Negative", 
                                                                                        "Negative",
                                                                                        "Neutral",
                                                                                        "Positive",
                                                                                        "Very Positive"))
perception_aq_stacked_bar$question <- factor(perception_aq_stacked_bar$question, levels = c("aquaculture",
                                                                                            "seaweed aquaculture"))

# percent stacked barchart
ggplot(data = perception_aq_stacked_bar, 
       aes(fill = forcats::fct_rev(answer),
           y = proportion,
           x = question)) +
  geom_bar(position = "stack",
           stat = "identity") +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values =c("#2C7BB6","#ABD9E9","#FFFFBF","#FDAE61","#D7191C","#C0C0C0")) +
  labs(x = "",
       y = "",
       title = "In general, how positive or negative is your view of ______ ?") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "right") #+
  #guides(color = guide_legend(reverse=TRUE),
  #       fill = guide_legend(nrow=1, byrow=TRUE))

```

```{r}
# Descriptive Statistics
perception_aq_stats <- survey_data_tidy_sbv_long_filtered %>% 
  select(question, answer) %>% 
  filter(question == "q12" |
           question == "q13") %>% 
  mutate(answer = case_when( 
    answer == "Very Negative" ~ -2,
    answer == "Negative" ~ -1,
    answer == "Neutral" ~ 0,
    answer == "Positive" ~ 1,
    answer == "Very Positive" ~ 2,
    answer == "Unsure/Not familiar" ~ -999)) %>%
  replace_with_na(replace = list(answer = -999)) %>% 
  drop_na() %>% 
  group_by(question) %>% 
  summarize(mean = mean(answer),
            median = median(answer),
            sd = sd(answer))
  
```

## Environmental Impacts

```{r}
# Environmental Impacts Questions

# Q23_1 - Q23_7
# To what extent do you agree with each of the following statements?

environ_impacts <- survey_data_tidy_sbv_long_filtered %>% 
  select(question, answer) %>% 
  filter(question == "q23_1" | 
           question == "q23_2" |
           question == "q23_3" |
           question == "q23_4" |
           question == "q23_5" |
           question == "q23_6" |
           question == "q23_7") %>% 
  mutate(question = case_when( 
    question == "q23_1" ~ "...has negative impacts on marine ecosystems.",
    question == "q23_2" ~ "...improves water quality nearby.",
    question == "q23_3" ~ "...infrastructure poses a risk to marine life.",
    question == "q23_4" ~ "...infrastructure has positive impacts on marine ecosystems.",
    question == "q23_5" ~ "...has positive impacts on marine ecosystems.",
    question == "q23_6" ~ "...causes bad smells nearby.",
    question == "q23_7" ~ "...is visually appealing.")) %>% 
  mutate(number = case_when( 
    answer == "Strongly Disagree" ~ 1,
    answer == "Disagree" ~ 2,
    answer == "Neutral" ~ 3,
    answer == "Agree" ~ 4,
    answer == "Strongly Agree" ~ 5,
    answer == "Don't know" ~ 6)) %>%
  #replace_with_na(replace = list(number = -999)) %>% 
  drop_na() %>%                                            # drop NAs (counts of those who skipped question)
  #mutate_all(na_if, "") %>% 
  group_by(question, answer, number) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  group_by(question) %>% 
  mutate(proportion = (count / sum(count))*100) %>% 
  ungroup() 

# Specify categorical order of answers
environ_impacts$answer <- factor(environ_impacts$answer, levels = c("Strongly Disagree", 
                                                                    "Disagree", 
                                                                    "Neutral",
                                                                    "Agree",
                                                                    "Strongly Agree",
                                                                    "Don't know"))

# percent stacked barchart
ggplot(data = environ_impacts, 
       aes(fill = forcats::fct_rev(answer), 
           x = proportion,
           y = question)) +
  geom_bar(position = "fill",
           stat = "identity") +
  scale_x_continuous(labels = scales::percent) +
  scale_y_discrete(position = "right") +
  scale_fill_brewer(type = "div",
                    palette = "RdYlBu",
                    direction = +1) +
  labs(x = "",
       y = "",
       title = "Seaweed Aquaculture...") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  guides(fill=guide_legend(nrow=1,byrow=TRUE))

```

## Economic Impacts


## Demographics 

```{r}
## Exploratory Plots

# Birth Year (Q31)
ggplot(data = survey_data_tidy, aes(y = q31)) +
  geom_bar()
### need to remove SB and NJ words from years

# Gender Identity (Q32)
ggplot(data = survey_data_tidy, aes(x = q32)) +
  geom_bar()

# Race/ethnicity (Q33)
ggplot(data = survey_data_tidy, aes(y = q33)) +
  geom_bar()
### how to deal with people selecting more than one option ????

# Highest level of education (Q34)
ggplot(data = survey_data_tidy, aes(y = q34)) +
  geom_bar()

# Annual household income (Q35)
ggplot(data = survey_data_tidy, aes(y = q35)) +
  geom_bar()

# Political Affiliation (Q38)
ggplot(data = survey_data_tidy, aes(y = q38)) +
  geom_bar()


```





## Communication Questions 

```{r}
# Q29_1 - Q29_6 (Rank the aquaculture related topics in order of interest in learning more, with 1 being most interested)

# q29_1 - policy
# q29_2 - permitting
# q29_3 - environmental impacts
# q29_4 - economic impacts
# q29_5 - social & cultural impacts
# q29_6 - research

# make new subset of data
comm_data <- survey_data_tidy %>% 
  select(q29_1:q29_6) %>% 
  mutate_if(is.character,as.numeric) %>% 
  summarize_all(mean, na.rm = TRUE) # calculate mean rank score for each answer choice
  #column_to_rownames(q29_1, "policy")

# transpose dataframe
comm_data <- t(comm_data) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "aquaculture_topics") %>% 
  mutate(aquaculture_topics = case_when(
    aquaculture_topics == "q29_1" ~ "policy",
    aquaculture_topics == "q29_2" ~ "permitting",
    aquaculture_topics == "q29_3" ~ "environmental impacts",
    aquaculture_topics == "q29_4" ~ "economic impacts",
    aquaculture_topics == "q29_5" ~ "social & cultural impacts",
    aquaculture_topics == "q29_6" ~ "research")) %>% 
  mutate(aquaculture_topics = fct_reorder(aquaculture_topics, V1, .desc = TRUE))  # order topics by count, smallest (most interested) to largest (least interested)

ggplot(data = comm_data, aes(x = aquaculture_topics, y = V1)) +
  geom_col(fill = "skyblue4") +
  coord_flip() +
  theme_minimal() +
  labs(x = "",
       y = "Average Ranked Score (from 1 - 6, with 1 being most interested)",
       title = "Aquaculture Topics Ranked by Interest in Learning More")


### need to add std dev or std error bars???
```

```{r}
# Q30_1 - Q30_6 (Rank the forms of communication by which you would prefer to learn about aquaculture, with 1 being most interested)

# q30_1 - short educational film
# q30_2 - physical pamphlets
# q30_3 - festivals/conferences
# q30_4 - website
# q30_5 - social media/blogs
# q30_6 - other
# q30_6_TEXT - (other text)

# make new subset of data
comm_data_2 <- survey_data_tidy %>% 
  select(q30_1:q30_6) %>% 
  mutate_if(is.character,as.numeric) %>% 
  summarize_all(mean, na.rm = TRUE) # calculate mean rank score for each answer choice

# transpose dataframe
comm_data_2 <- t(comm_data_2) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "form_of_communication") %>% 
  mutate(form_of_communication = case_when(
    form_of_communication == "q30_1" ~ "short educational films",
    form_of_communication == "q30_2" ~ "physical pamphlets",
    form_of_communication == "q30_3" ~ "festivals/conferences",
    form_of_communication == "q30_4" ~ "website",
    form_of_communication == "q30_5" ~ "social media/blogs",
    form_of_communication == "q30_6" ~ "other")) %>% 
  mutate(form_of_communication = fct_reorder(form_of_communication, V1, .desc = TRUE))  # order topics by count, smallest (most interested) to largest (least interested)

ggplot(data = comm_data_2, aes(x = form_of_communication, y = V1)) +
  geom_col(fill = "skyblue4") +
  coord_flip() +
  theme_minimal() +
  labs(x = "",
       y = "Average Ranked Score (from 1 - 6, with 1 being most interested)",
       title = "Ranked Forms of Communication")


### need to add std dev or std error bars???

```

```{r}
## Word Cloud list of "other" forms of communication

# convert each string of words to lowercase
survey_data_tidy$q30_6_text <- tolower(survey_data_tidy$q30_6_text)

other_comm_forms <- survey_data_tidy %>% 
  select(q30_6_text) %>%
  mutate(q30_6_text = str_trim(q30_6_text)) %>%  # remove excess whitespace before/after word
  count(q30_6_text) %>%                          # count repeating words
  arrange(-n)                                    # arrange word counts from largest to smallest

wordcloud_other_comm_forms <- ggplot(data = other_comm_forms, 
                                    aes(label = q30_6_text)) +
  geom_text_wordcloud(aes(color = n, size = n), 
                      shape = "diamond") +
  scale_size_area(max_size = 80) +
  scale_color_gradientn(colors = c("burlywood4", "green")) +
  theme_minimal() +
  labs(y = "other forms of communication") +
  theme(axis.line.y = element_line(color="black", size = 0.1))

wordcloud_other_comm_forms
```











## Citations: 

California county boundaries layer: [US Census Bureau's 2016 MAF/TIGER database.](https://data.ca.gov/dataset/ca-geographic-boundaries)

California ZIP code tabulations areas layer: [US Census Bureau's 2020 TIGER/Line Shapefiles database.](https://www.census.gov/cgi-bin/geo/shapefiles/index.php?year=2021&layergroup=ZIP+Code+Tabulation+Areas)

zipcode R package []
(https://cran.r-project.org/web/packages/zipcodeR/zipcodeR.pdf)



