---
title: "statsistical_tests_jg"
author: "Janelle Gaun"
date: "1/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(data.table)  # advanced pivot_table tools
library(naniar)      # replace NA tools
#library(sf)          # read in shapefiles
#library(tmap)        # interactive maps
#library(zipcodeR)    # for zipcode assignment by county
#library(raster)      # for mapping raster layers
#library(dplyr)       # needed ONLY if working on a windows computer
#library(ggwordcloud) # create wordcloud plots
library(patchwork)   # for stacking plots
library(kableExtra)  # for making tables
library(broom)
library(MASS)         #for ordered logist or probit regression
library(conflicted)  # allows for choosing preference over conflicting functions from different packages
library(RColorBrewer)
conflict_prefer("select", "dplyr") # use select function from tidyverse/dplyr package > from raster package
conflict_prefer("filter", "dplyr")
conflict_prefer("chisq.test", "janitor")
conflict_prefer("fisher.test", "janitor")
```

```{r}
#load in compiled data files 

survey_data_tidy_sbv_filtered <- read.csv(here("data", "survey_data_tidy_sbv_filtered.csv"))

survey_data_tidy_sbv_long_filtered <- read.csv(here("data", "survey_data_tidy_sbv_long_filtered.csv"))
```

## Knowledge 

We test the relationship between people's familiarity with aquaculture and their perceptions of seaweed aquaculture using a chi-squared test. 

*10 & 13. perception and Familiarity* 

*Question:* Does familiarity with aquaculture influence their  of aquaculture? 

*Null Hypothesis (H0):*  There is no association between the two variables (familiarity and perceptions) i.e. they are independent 

*Statistical Test:* Chi-square test of Q10 & Q13

*Test Statistic:* P-value > 0.5 

#### Q10 (familiarity) v. Q13 (perception of swaq)
```{r 10v.13 dataframe, table and plot}
#create subset from tidy filtered data
#keep only question 10 and 13
k_p <- survey_data_tidy_sbv_long_filtered %>% 
  select(response_id, question, answer) %>% 
  filter(question == "q10"|
           question == "q13") %>% 
#switch to wide format with response id as the link
 spread(question, answer) %>% 
  mutate(q13 = fct_relevel(q13, c(c("Very Negative", "Negative","Neutral","Positive", "Very Positive", "Unsure/Not familiar")))) %>% 
  mutate(q10 = fct_relevel(q10, c(c("Very familiar", "Basic understanding", "Heard of it, but don't know details", "Never heard of it"))))

ggplot(k_p, aes(fill= q13, x = q10))+
  geom_bar(position = "dodge")+
  scale_x_discrete(labels= function(x) str_wrap(x, width = 10))+
  scale_fill_manual(values =c("#D7191C", "#FDAE61", "#FFFFBF", "#ABD9E9","#2C7BB6", "#999999"))
  
#put counts into table format
k_p_table<- k_p %>% 
  tabyl(q10, q13) 
```

One key assumption of the chi-square test is that 80% of the cells must have an expected value of 5 or greater. Only 14 of the 24 cells meet this requirement (58%), therefore violating the assumptions of the chi-square test. We will use the maximum liklihood chi-square test to also understand the relationship bewteen the two variables. 


```{r 10 v. 13 chi squared test}
# Use `column_to_rownames` to convert counts table to a contingency table (makes `q10` column entries into stored rownames)
k_p_ct <- k_p_table %>% 
  column_to_rownames(var = "q10")

# Chi-square test for independence: Is there an association between support for aquaculture and word choice?
knowledge_perception_x2 <- chisq.test(k_p_ct)
knowledge_perception_x2

# Get the chi-square test results to call outputs in-line
k_p_x2_tidy <- tidy(knowledge_perception_x2)
```

The p-squared value `r round(k_p_x2_tidy[1, 2], 2)` is less than alpha (0.05) indicating the null hypothesis- that the two variables are independent- failed. However, there were some counts that were less than 5 which indicates there should be additional study. However, the data violates an assumption of the chi-square test so we conduct the maximum likelihood test below. 

We will aggregate 'very negative' and 'negative' and 'very positive' and 'postiive' and run the chi-square with these groups. 

```{r group Q13 responses}
#create subset from tidy filtered data
#keep only question 10 and 13
k_p_grouped <- survey_data_tidy_sbv_long_filtered %>% 
  select(response_id, question, answer) %>% 
  filter(question == "q10"|
           question == "q13") %>% 
#switch to wide format with response id as the link
 spread(question, answer) %>% 
#group responses
    mutate(q13= case_when(
    q13 == "Very Negative" ~ "Negative",
    q13 == "Negative" ~ "Negative",
    q13 =="Neutral" ~ "Neutral",
    q13 == "Positive" ~ "Positive",
    q13 =="Very Positive" ~ "Positive",
    q13 =="Unsure/Not familiar" ~ "Unsure/Not familiar",
  ))

#ggplot(k_p, aes(fill= q13, x = q10))+
 # geom_bar(position = "dodge")+
  #scale_x_discrete(labels= function(x) str_wrap(x, width = 10))+
  #scale_fill_manual(values =c("#D7191C", "#FDAE61", "#FFFFBF", "#ABD9E9","#2C7BB6", "#999999"))
  
#put counts into table format
k_p_grouped_table<- k_p_grouped %>% 
  tabyl(q10, q13) 
```

```{r Q13 grouped chi-squared}
k_p_grouped_ct <- k_p_grouped_table%>% 
  column_to_rownames(var = "q10")

# Chi-square test for independence: Is there an association between support for aquaculture and word choice?
knowledge_perception_grouped_x2 <- chisq.test(k_p_grouped_ct)
knowledge_perception_grouped_x2

```

When perception is combined into 'negative', 'neutral', 'positive', and 'unsure', the null hypothesis is rejected (p-value= 2.22 x10-7, alpha =0.05) which indicates the variables are dependent. 

We can also  the Fischer's exact test to calculat the exact p-value. **Fisher's test requires a high muber of simulations because the value of p is so small. Kept crashing R**

```{r 10 v. 13 Fischer's exact test}
#fisher.test(k_p_ct, workspace = 2e7)
```

#### Q16 (heard about aq) v. Q13 (perception)

```{r dataset Q16(heard of aq) v Q13 }
#create subset from tidy filtered data
#keep only question 16 and 13
k_p_heard <- survey_data_tidy_sbv_long_filtered %>% 
  select(response_id, question, answer) %>% 
  filter(question == "q16"|
           question == "q13") %>% 
#switch to wide format with response id as the link
 spread(question, answer) %>% 
  #group responses
  mutate(q13= case_when(
    q13 == "Very Negative" ~ "Negative",
    q13 == "Negative" ~ "Negative",
    q13 =="Neutral" ~ "Neutral",
    q13 == "Positive" ~ "Positive",
    q13 =="Very Positive" ~ "Positive",
    q13 =="Unsure/Not familiar" ~ "Unsure/Not familiar",
  ))

ggplot(k_p_heard, aes(fill= q13, x = q16))+
  geom_bar(position = "dodge")+
  scale_x_discrete(labels= function(x) str_wrap(x, width = 10))+
  scale_fill_manual(values =c("#D7191C", "#FFFFBF", "#2C7BB6", "#999999"))
  
#put counts into table format
k_p_heard_table<- k_p_heard %>% 
  tabyl(q16, q13) 
```

```{r 16 v. 13 chi squared test}
# Use `column_to_rownames` to convert counts table to a contingency table (makes `q10` column entries into stored rownames)
k_p_heard_ct <- k_p_heard_table %>% 
  column_to_rownames(var = "q16")

# Chi-square test for independence: Is there an association between support for aquaculture and word choice?
k_p_heard_x2 <- chisq.test(k_p_heard_ct)
k_p_heard_x2

# Get the chi-square test results to call outputs in-line
k_p_x2_tidy <- tidy(k_p_heard_x2)
```

The data violate the assumptions of the chi-square test (80% of the expected values >5). The fisher exact test will be used instead. 

```{r 16 v. 13 fisher test}
# Use `column_to_rownames` to convert counts table to a contingency table (makes `q10` column entries into stored rownames)

fisher_Q16 <- fisher.test(k_p_heard_ct)
fisher_Q16 <- tidy(fisher_Q16)
```

The null hypothesis was rejected using the Fisher exact test (p-value = 3..7x10-7, alpha =0.05). There is a relationship between hearning about aquaculture perceptions of aquaculture.

#### Q17 (seen aq) v. Q13 (perception)

```{r dataset Q16(heard of aq) v Q13- grouped}
#create subset from tidy filtered data
#keep only question 16 and 13
k_p_seen <- survey_data_tidy_sbv_long_filtered %>% 
  select(response_id, question, answer) %>% 
  filter(question == "q17"|
           question == "q13") %>% 
#switch to wide format with response id as the link
 spread(question, answer) %>% 
  #group responses
  mutate(q13= case_when(
    q13 == "Very Negative" ~ "Negative",
    q13 == "Negative" ~ "Negative",
    q13 =="Neutral" ~ "Neutral",
    q13 == "Positive" ~ "Positive",
    q13 =="Very Positive" ~ "Positive",
    q13 =="Unsure/Not familiar" ~ "Unsure/Not familiar",
  ))

ggplot(k_p_seen, aes(fill= q13, x = q17))+
  geom_bar(position = "dodge")+
  scale_x_discrete(labels= function(x) str_wrap(x, width = 10))+
  scale_fill_manual(values =c("#D7191C", "#FFFFBF", "#2C7BB6", "#999999"))
  
#put counts into table format
k_p_seen_table<- k_p_seen %>% 
  tabyl(q17, q13) 
```

The data did not meet the assumptions of the chi-sqare test(80% of expected values >5). Data was tested using the Fisher exact test instead. 

```{r 17 v. 13 fishertest}
# Use `column_to_rownames` to convert counts table to a contingency table (makes `q10` column entries into stored rownames)
k_p_seen_ct <- k_p_seen_table %>% 
  column_to_rownames(var = "q17")

fisher_Q17 <- fisher.test(k_p_seen_ct)
fisher_Q17 <- tidy(fisher_Q17)
```


The Fisher exact test rejected the null hypothesis- that the two variables are independent (p-vale= 0.031, alpha =0.05). 
















































## Regression Models : Relationship between Knowledge and Support 
####Relationship Between knowledge and support

*Question:* Is support related to more familiarity/knowledge of seaweed aquaculture?

*Hypothesis:* Those who are familiar with aquaculture will have more polarized opinions. Those less familiar will have more positive views of kelp aquaculture. 

*Assumptions:* 
- Since Q2,4, 6, 8 are not significantly different, then questions/answers can thus be combined.
- Remove "don't know" answer choice counts

*Statistical Test:* Ordinal logistic regression of perception combined support values (Q2,4,6,8) vs. perception of seaweed aquaculture (Q13)

dependent variable = support (Q2)
independent variable = perception (Q13)


```{r regression table }
# create data frame with Q2 and Q10

ordinal_log_reg_knowledge_data <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8" |
         question == "q13") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2",
    question == "q13" ~ "q13")) %>% 
  mutate(answer = case_when( 
    answer == "Strongly opposed" ~ -2,
    answer == "Somewhat opposed" ~ -1,
    answer == "Neither opposed nor in support" ~ 0,
    answer == "Somewhat supportive" ~ 1,
    answer == "Strongly supportive" ~ 2,
    answer == "Very Positive" ~ 2,
    answer == "Positive" ~ 1,
    answer == "Neutral" ~ 0,
    answer == "Negative" ~ -1,
    answer == "Very NegativeNegative" ~ -2,
    answer == "Unsure/Not familiar" ~ -999)) %>%
  replace_with_na(replace = list(answer = -999))%>% 
  filter(answer != "NA") # remove incomplete responses

```

```{r}
# use spread() to pivot table to wide format
ordinal_log_reg_knowledge <- ordinal_log_reg_knowledge_data %>% 
  select(response_id, question, answer) %>% 
  spread(question, answer) %>% 
  filter(q13 != "NA")  %>% # remove incomplete responses
  filter(q2 != "NA") # remove incomplete responses
  
ordinal_log_reg_knowledge_table<- ordinal_log_reg_knowledge %>% 
  tabyl(q2, q13) %>% 
  column_to_rownames(var = "q2")

summary(ordinal_log_reg_knowledge_table)

```


```{r create ordinal logistic model}
#use polr to create a logit model to understand how familiarity influences expansion
m2 <- polr(factor(q2) ~q13, data=ordinal_log_reg_knowledge, Hess =TRUE)
summary(m2)
```


```{r understand odds ratio}
#interpret odds ratio. Outside parenthesis are important 
(ci <- confint(m2))
exp(cbind(coef(m2), t(ci)))
```


```{r predicted probabilities to understand odds ratio}
newdf_2 <- data.frame(q13 =c(1, 2, 3, 4, 5))
(phat <- predict(object = m2, newdf_2, type = "p"))
```


























####Relationship Between Perception and Support: 


*Question:* Is support related to more positive perceptions of seaweed aquaculture?

*Hypothesis:* Yes, supporters will have more positive perceptions of seaweed aquaculture.

*Assumptions:* 
- Since Q2,4, 6, 8 are not significantly different, then questions/answers can thus be combined.
- Remove "don't know" answer choice counts

*Statistical Test:* Ordinal logistic regression of perception combined support values (Q2,4,6,8) vs. perception value from Q13 (seaweed aquaculture)


dependent variable = support (Q2)
independent variable = knowledge (Q10)


```{r regression table }
# create data frame with Q2 and Q10

ordinal_log_reg_2_data <- survey_data_tidy_sbv_long_filtered %>% 
  filter(question == "q2" | 
         question == "q4" |
         question == "q6" |
         question == "q8" |
         question == "q10") %>%
  mutate(question = case_when( 
    question == "q2" ~ "q2",
    question == "q4" ~ "q2",
    question == "q6" ~ "q2",
    question == "q8" ~ "q2",
    question == "q10" ~ "q10")) %>% 
  mutate(answer = case_when( 
    answer == "Strongly opposed" ~ -2,
    answer == "Somewhat opposed" ~ -1,
    answer == "Neither opposed nor in support" ~ 0,
    answer == "Somewhat supportive" ~ 1,
    answer == "Strongly supportive" ~ 2,
    answer == "Very familiar" ~ 1,
    answer == "Basic understanding" ~ 2,
    answer == "Heard of it, but don't know details" ~ 3,
    answer == "Never heard of it" ~ 4)) %>%
  filter(answer != "NA") # remove incomplete responses

```

```{r}
# use spread() to pivot table to wide format
ordinal_log_reg_2 <- ordinal_log_reg_2_data %>% 
  select(response_id, question, answer) %>% 
  spread(question, answer) %>% 
  filter(q10 != "NA")  %>% # remove incomplete responses
  filter(q2 != "NA") # remove incomplete responses
  
ordinal_log_reg_2_table<- ordinal_log_reg_2 %>% 
  tabyl(q2, q10) %>% 
  column_to_rownames(var = "q2")

summary(ordinal_log_reg_2_table)

```


```{r create ordinal logistic model}
#use polr to create a logit model to understand how familiarity influences expansion
m1 <- polr(factor(q2) ~q10, data=ordinal_log_reg_2, Hess =TRUE)
summary(m1)
```


```{r understand odds ratio}
#interpret odds ratio. Outside parenthesis are important 
(ci <- confint(m1))
exp(cbind(coef(m1), t(ci)))
```


```{r predicted probabilities to understand odds ratio}
newdf <- data.frame(q10 =c(1, 2, 3, 4))
(phat <- predict(object = m1, newdf, type = "p"))
```

































